---
title: Example Script
editor_options:
  chunk_output_type: console
output:
  html_document:
    fig_caption: yes
    figure_caption: yes
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Headline without Number {-} 
the number is not displayed due to the use of {-}

# Headline 1
## Headline 2 {#name_test}
### Headline 3
#### Headline 4
##### Headline 5
Here you can see that headlines 4 + 5 is not displayed in the TOC above. This is based on "toc_depth: '3'" what we wrote in the Markdown YAML header  

The different headers can also get names (see Headline 2 in the Markdown)  
These can be used to enter jumps to the respective [headline](#name_test)

When writing text, you can create a new line  
by adding two spaces at the end.  

Without two spaces everything will 
be in one line.

# create unordered lists

* list 1 - item 1
* list 1 - item 2
  + list 1 - item 2.1
  + list 1 - item 2.2
    - list 1 - item 2.2.1
    
For each level you have to enter an additional tab

# create ordered lists

1. list 2 - item 1
2. list 2 - item 2
   1. list 2 - item 2.1
   b. list 2 - item 2.2
      5. list 2 - item 2.2.1

Here, to have a second level you need to enter a tab and a space, for level 3 you need to enter two tabs and two spaces

# enter text in different formats

## italics
section needs to be frames by single ' * ' or ' _ '  
either *italics* or _italics_

## bold
section needs to be frames by double ' * ' or ' _ *  
either **bold** or __bold__

## subscript
section needs be framed by  ' ~ '  
e.g. H~2~O

## superscript
section needs to be framed by ' ^ '  
e.g. H^+^

combined example:
NH~4~^+^


# create Tables


First column | Second column
-|-
First row | First row
Second row | Second row

# Enter Links

you can enter links by either adding the link in ' < > ' or setting the hyperlinkable word in square brackets and the link in round brackets (without space in between)   
examples:
<https://www.uni-koblenz-landau.de>  
[Uni](https://www.uni-koblenz-landau.de)


# enter in-line R code
to enter in-line R code you have to set these in `` and start with an r

example:

Instead of writing manually 2 + 2 = 4  
you could write 2 + 2 = `r 2+2`


# enter in-line Latex code
you can also enter in-line Latex code, when for example planning to enter special characters

examples:  
alpha: $\alpha$  
beta: $\beta$  
phi: $\phi$  

using mouse over, you can have an immediate look if your Latex code is correct

like that you can also enter in-line equations

an example would be $y = x^2$


# enter equations in seperate lines
you also also enter Latex based equations in separate lines  
to do that, you need to use two $. You will also get an immediate preview of your equation
 
$$ k_{OW} = log \left( \frac{c_{1-octanol}}{c_{water}} \right)   $$


# Some other options

Enter dates:  
`r format(Sys.time(), "%d.%m.%Y")`

Enter information about your dataframe:  
`r nrow(mtcars)`  
`r ncol(mtcars)`


# Options for code chunks

To see what the different options are doing, we are using the example dataframe mtcars

You can (you don't need to) give chunks a name, to correctly identify the respective code chunks   
Double chunk names, however, are prohibited.  

## hiding code 
```{r chunk_hide_code, echo = FALSE}
cor.test(mtcars$mpg, mtcars$drat)

cor.test(mtcars$am, mtcars$gear)
```

## hiding result
```{r chunk_hide_result, echo = TRUE, results='hide'}
cor.test(mtcars$cyl, mtcars$hp)
```


## display all results at the end of a chunk
```{r chunk_result_end, results = 'hold'}
cor.test(mtcars$drat, mtcars$carb)

cor.test(mtcars$vs, mtcars$wt)

cor.test(mtcars$qsec, mtcars$disp)
```


## hiding messages
Here message is displayed
```{r chunk_show_messages, message = TRUE}
library(dplyr)
```


now we detach the package
```{r}
detach("package:dplyr", unload=TRUE)
```

and load it again, this time without message, but with warning
```{r chunk_hide_messages, message = FALSE}
library(dplyr)
```

now without message + warning
```{r chunk_hide_messages_warnings, message = FALSE, warning = FALSE}
detach("package:dplyr", unload=TRUE)
library(dplyr)
```


# Add figures
```{r figure}
plot(mtcars$mpg, mtcars$drat)
```

